\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-28 Paper/Paper.tex
add OCT_Abnormities.png

	The Abnormity Models are classifiers for abnormities, which are symptoms that can be directly observed in the images. The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:abnormities}. Also refer to ``Appendix'' for more details.

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/Temp.png}
		\caption{OCT and Fundus Abnormities}
		\vspace{0.3cm}
		\label{fig:abnormities}
	\end{figure}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.png}
		\caption{GradCAM}
		\vspace{0.3cm}
		\label{fig:gradCAM}
	\end{figure}
	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
		\caption{GradCAM with multiple abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM_multi_abnormity}
	\end{figure}

>>>>

	The Abnormity Models are classifiers for abnormities, which are symptoms that can be directly observed in the images. The MAAM identifies 11 OCT abnormities and 8 Fundus abnormities, as shown in Fig.~\ref{fig:OCT_abnormities} and Fig.~\ref{fig:fundus_abnormities}. Also refer to ``Appendix'' for more details.

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/OCT_Abnormities.png}
		\caption{OCT Abnormities}
		\vspace{0.3cm}
		\label{fig:OCT_abnormities}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/Temp.png}
		\caption{Fundus Abnormities}
		\vspace{0.3cm}
		\label{fig:fundus_abnormities}
	\end{figure}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_gradCAM.png}
		\caption{GradCAM}
		\vspace{0.3cm}
		\label{fig:gradCAM}
	\end{figure}
	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/abnormity_gradCAM_multiple_abnormities.png}
		\caption{GradCAM with multiple abnormities}
		\vspace{0.3cm}
		\label{fig:gradCAM_multi_abnormity}
	\end{figure}
